---
title: "Homework 1: Quarto, Basic Syntax and Data Importing"
subtitle: "Spring 2024 MATH/COSC 3570 Introduction to Data Science by Dr. Cheng-Han Yu"
format: 
  html:
    code-fold: false
    code-tools: true
    toc: true
    toc-depth: 3
date: today
author: "**Insert Your Name!!**"
number-sections: true
editor: 
  source
---

```{r}
#| label: setup
#| include: false

####################################################
## !!!DO NOT MAKE ANY CHANGE OF THIS CODE CHUNK!!!##
####################################################

pkgs <- c("knitr","rmarkdown", "tidyverse", "reticulate", "readxl", "ggplot2", "ggrepel")
lapply(pkgs, require, character.only = TRUE)
```

## Autobiography

(@) Please introduce yourself. You can share anything, your hometown, major, family, hobbies, working experience, honors and awards, special skills, etc, yes anything! Your autobiography should include:

    -   At least two paragraphs (Paragraphs are separated by a blank line)
    -   Bold text
    -   Italic text
    -   Text with both **bold AND italic** font (Not mentioned in class, but you should be able to figure it out)
    -   Clickable text with a hyperlink
    -   Blockquote
    -   Listed items
    -   emoji (Add emoji to your writing by typing `:EMOJICODE:`, check [emoji cheatsheet](https://github.com/ikatyang/emoji-cheat-sheet/blob/master/README.md))


    **Your Self-Introduction:**







## Chunk Options

Please check the references <https://quarto.org/docs/reference/cells/cells-knitr.html> or <https://yihui.org/knitr/options/> and answer the following questions.

(@)  Please add your nice picture using `knitr::include_graphics()`. Please use
    i) `echo` to not to show the code
    
    ii) `fig-cap` to add a figure caption
    
    iii) `fig-cap-location` to put the caption on the margin.

```{r}
#| label: photo


```

(@)  Use the chunk option 
    i) `echo` to **NOT** to show `library(tidyverse)`, `library(ggplot2)`, and `library(ggrepel)`. *Note: you may need to use !expr. Check <https://stackoverflow.com/questions/72217651/quarto-rmarkdown-code-block-to-only-display-certain-lines> and <https://quarto.org/docs/computations/r.html#chunk-options>*
    
    ii) `fig-align` to have the figure right-aligned. 

    ```{r}
    #| label: opt-echo
    
    library(tidyverse)
    library(ggplot2)
    class_avg <- mpg |> 
        group_by(class) |> 
        summarise(displ = median(displ), hwy = median(hwy))
    library(ggrepel)
    ggplot(mpg, aes(displ, hwy, colour = class)) + 
        geom_label_repel(aes(label = class), data = class_avg, size = 6, 
                         label.size = 0, segment.color = NA) + 
        geom_point() + theme(legend.position = "none")
    ```


(@)  A Marquette student has a really bad code style. Please 
    i) Add the chunk option `tidy` in the chunk labelled `style` to make her code below more readable. 
    
    ii) Add another option `eval` so that the code is **NOT** run.

```{r}
#| label: style

for(k in 1:10){j=cos(sin(k)*k^2)+3;l=exp(k-7*log(k,base=2));print(j*l-5)}
```

(@)  Use the chunk option `results` in the chunk labelled `cat`, so that the text output is "I love **Marquette** and *Data Science*!".

```{r}
#| label: cat

cat("I love **Marquette** and *Data Science*!\n")
```

(@)  We can re-use a code chunk by using its name! Please create a code chunk and use the option `#| label: photo` to run the code in the code chunk named `photo`. Note that the chunk options are not carried.

```{r}

```

## Basic R

### Vector

Use the built-in data set `LakeHuron`.

(@)  Find the number of data values in `LakeHuron`.

```{r}
#| label: vec-1

```

(@)  What is the highest and lowest level (in feet) of LakeHuron during the 1875-1972 period?

```{r}
#| label: vec-2

```

(@)  Return a logical vector that shows whether the lake level is higher than the average level or not.

```{r}
#| label: vec-3

```

(@)  Return years that have higher level than the average.

```{r}
#| label: vec-4

```

### Data Frame

(@)  Make the `mtcars` dataset as a tibble using `as_tibble()`. Call it `tbl`.

```{r}
#| label: df-2


```

(@)  Print the sub data of `tbl` that contains the 11th to 15th rows and the last three columns.

```{r}
#| label: df-3


```

(@)  Grab the second and the third columns of `tbl` using *list* method and their *name*. (Do **NOT** use matrix method, and their index)

```{r}
#| label: df-4


```

(@)  Extract the fourth column of `tbl` as a numerical vector.

```{r}
#| label: df-5


```

(@)  Start with `tbl`, use the pipe operator `|>` to do the followings sequentially.

    i.  extract the first 10 observations (rows)
    
    ii. find the column names
    
    iii. sort the columns names using `sort()` in a *decreasing* order. (alphabetically from z to a)

```{r}
#| label: df-6


```

### Data Importing

(@)  Read the data `sales.xlsx` from the data folder. Use arguments `sheet`, `skip` and `col_names` so that the output looks like

        # A tibble: 9 x 2
          id      n    
          <chr>   <chr>
        1 Brand 1 n    
        2 1234    8    
        3 8721    2    
        4 1822    3    
        5 Brand 2 n    
        6 3333    1    
        # … with 3 more rows

```{r}
#| label: import-1


```

(@)  Read in the `favourite-food.xlsx` file from the data folder and call the data `fav_food`. Use the argument `na` to treat "N/A" and "99999" as a missing value. Print the data out.

```{r}
#| label: import-2


```

## Basic Python

```{python}
import numpy as np
import pandas as pd
```

### Data Frame

(@)  Import the data set `mtcars.csv` using `pd.read_csv()`. Then print the first five rows.

```{python}
#| label: py-1


```

(@)  Use method `.iloc` to obtain the first and fourth rows, and the second and third columns. Name the data `dfcar`.

```{python}
#| label: py-2


```

(@)  Set the row names of `dfcar` to `Mazda` and `Hornet`.

```{python}
#| label: py-3


```

(@)  Use method `.loc` to obtain row `Hornet` and column `disp`.

```{python}
#| label: py-4


```




